The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-03-30 ms.Rmd
Make knitr cache output.

```{r knitrOpts, echo = FALSE, cache = FALSE, eval = TRUE}
opts_chunk$set(fig.path = 'figs/', message = FALSE, dev = c('pdf', 'png'))

@@

# add a panel letter
# this is an awful hack and completely contingent on the screenshot size :/
text(40, 980, labels = LETTERS[1],
      xpd = NA,
     cex = 1.2)

>>>>

```{r knitrOpts, echo = FALSE, cache = FALSE, eval = TRUE}
opts_chunk$set(fig.path = 'figs/', message = FALSE, dev = c('pdf', 'png'), cache = TRUE)

@@

# add a panel letter
# this is an awful hack and completely contingent on the screenshot size :/
text(40, 940, labels = LETTERS[1],
      xpd = NA,
     cex = 1.2)
